### 2014-03-20 paper/designspace.tex
addressing bjoern and tovi comments

\section{The Design Space of Pipes}
\bjoern{We should be careful with our terminology - apparently pipes and pipes have different connotations. Pipes are measured by outer diameter (OD) and tend to be structural, while pipes are measured by inside diameter (ID) and tend to be used to transport media inside them. At the least, we should mention that different communities have these different connotations. I think that in our case, we're thinking mostly of the 3D print as the structural object that we're then tunneling through with {\em pipes}.}

We propose the use of pipes to redirect active components through the core and onto the surface of 3D printed interactive objects, as well as to allow for the creation of designed paths.  By using different types and topologies of pipes and inserting different media into the completed pipes, a variety of inputs and outputs can be located at arbitrary points on the surface of a 3D print.  We describe the design space of pipes, and then follow up with some of the input and output possibilities---both those that have been previously explored and those that are possible but remain unexplored.

>>>>

\section{The Design Space of Pipes}
We propose the use of pipes to redirect active components through the core and onto the surface of 3D printed interactive objects, as well as to allow for the creation of designed paths.  By using different types and topologies of pipes and inserting different media into the completed pipes, a variety of inputs and outputs can be located at arbitrary points on the surface of a 3D print.  We describe the design space of pipes, and then follow up with some of the input and output possibilities---both those that have been previously explored and those that are possible but remain unexplored.

### 2014-03-20 paper/introduction.tex
addressing bjoern and tovi comments

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{Here's a teaser figure of some cool stuff we did. Probably it should show one of our example objects, or we can make it really big (figure*) and show them all!}
\label{fig:teaser}
\end{figure}

\section{Introduction}
Makers, as well as professional designers, leverage 3D printers as tools for design work.  A wide array of objects, ranging from bicycle helmets to jewelry to video game controllers, are now prototyped or even manufactured using these machines.  However, most devices fabricated by 3D printers are passive: accessible printers are not yet capable of creating integrated active systems. \bjoern{not sure I understand phrase after the colon. Rewrite and explain what you mean in more detail?}

Willis, et al., ``envision a future world where interactive devices can be printed rather than assembled; a world where a device with active components is created as a single object, rather than a case enclosing circuit boards and individually assembled parts" \cite{Willis-printedoptics}.  This is a vision we eagerly share: 3D printers are capable of creating arbitrary geometries not feasible to manufacture using traditional processes, and we see these capabilities being underutilized by makers and designers.  We see many opportunities to increase the interactivity of 3D prints using today's printer technology.
\tovi{Might want some examples of what possibilities this opens up}
\bjoern{I think we're doing something a little different from Karl's vision - in all of our examples, you need to hook up extra sensors, actuators, or lights to the 3D-printed object. So there's always still assembly required. We're not really printing interactive objects in a single pass, but we're offering new ways of adding interactivity to 3D printed objects.

I'd argue the principal novelty of our work is to {\em remove material} from a model to form pipes and other cavities. We demonstrate how designers/makers can then use these pipes, e.g. by filling them with various media to enable input, display and tactile feedback. This {\em subtractive} approach is complementary to {\em additive} approaches that try to print different materials such as conductors. While our approach requires manual assembly afterwards, it opens up a large useful design space on commonly available 3D printers.}

Using specially modified printers or extra machinery, it is possible to create electronics on the surface of 3D prints \cite{optomec} \cite{Sells-reprap}.  These techniques, however, require a high capital investment and technical expertise.  In addition, they lack flexibility: the printed circuits must be routed in 2D to be created on the objects' manifold exteriors, and they can only be used to create electronic circuits. \valkyrie{what?}  \tovi{I dont follow this paragraph - I think you want  to briefly summarize what has been previousl done in interactive 3d prints, and hihglight the shortcommings and remianing challenges} \bjoern{agree. Also, probably too much focus on electronics since it's only one of a series of examples we'll demonstrate.}

In addition to electronics, many other means of interactivity exist.

\valkyrie{Points to hit: there is more than electronics to worry about, like fluids and the organic haptic feedback they afford; tangible interfaces are important (do I have to say this every time??); assembly sucks}

In this paper, we propose a new technique, where interior channels, such as hollow chambers or solid \bjoern{?}, are integrated into 3D models. Such channels introduces a entire design space of opportunities for adding interactvity to 3D printed objects. For example, copper material can fill the channels, to allow for standard electronic components to be easily integrated after the printout; air can be pumped through to create tactile output; or, Electroluminescent wire can be passed through to create interactive visual output. \bjoern{this is good - I'd make this the central argument of the intro and move it up earlier.}

Our work makes the following contributions to the field of interactive digitial fabrication. First, ... design space...Second ... modeling tool and algorithms ... Third showcase a set of examples, enabled by our modeling tool. \bjoern{I'd say more about the software contribution in the abstract. Maybe that just requires expanding these notes into a full paragraph.}

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/teaser.png}
\caption{A novel neon sign (a) and a touch-sensitive brain (b) designed with our pipe tool and fabricated on a consumer-grade 3D printer.  (c) and (d) show the structure of the internal pipes generated by our tool.}
\label{fig:teaser}
\end{figure}

\section{Introduction}

Makers, as well as professional designers, leverage 3D printers as tools for design work.  A wide array of objects, ranging from bicycle helmets to jewelry to video game controllers, are now prototyped or even manufactured using these machines.  However, most devices fabricated by 3D printers are passive.  We propose a novel technique involving the removal of material from the interior of 3D models, prior to printing, to create pipes and other cavities.  These pipes can be filled, post-print, by a variety of media that enable input, display, and tactile feedback.  This {\em subtractive} approach is complementary to {\em additive} approaches that try to print different materials, such as conductors. While our approach requires manual assembly afterwards, it opens up a large useful design space on commonly available 3D printers, allowing makers to create objects like those in Figure \ref{fig:teaser}.

These channels introduce an entire design space of opportunities for adding interactivity to these objects. For example, copper material can fill the channels, to allow for standard electronic components to be easily integrated after the printout; air can be pumped through to create tactile output; or electroluminescent wire can be threaded through to create computer-controlled visual output.

The use of pipes can allow for \emph{redirection} and \emph{centralization} of active components, which creates \emph{iterable} devices.  For example, to create a touch-sensitive toy as in Figure \ref{fig:teaser}, a maker can select several locations of interest on the surface of the brain.  After creating pipes to those locations and printing her object, she can fill the pipes with conductive paint.  For sensing, she need only connect a single wire to a shared out of all the tubes, and can distinguish them via Swept Frequency Capacitve Sensing \cite{Sato-touche}.  If she decides that another area of interest is important to distinguish, she can simply print a new model with a new pipe leading to that location: the electronics assembly remains the same and she need only connect the same single wire to the tube out.  \valkyrie{not clear that this is our contribution.}

Pipes can also be used for sending media on a specified route through an object; for example, neon signs are created by evacuated glass tubes formed into a specific path.  Electricity is run through the near-vacuum, and this makes the path visible.  If our maker wants to build such a sign, she can substitute Electroluminescent (EL) wire for the evacuated glass and electricity: she need only design a path for the wire to be fed through and then create pipes along that path.

The generation of these pipes, however, is not trivial.  Pipes need to be as straight as possible to ease the insertion of media post-print.  Independent pipes should not intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface (unless they are being used for display purposes), especially since consumer-grade 3D printers do not guarantee air- or water-tightness of their prints, so more than one layer may be required to prevent leakage.

Our work makes the following contributions to the field of digitally fabricated interactive objects:

\begin{itemize}
\item We lay out a design space of pipe-mediated interactive possibilities. 
\item We offer algorithms and techniques for routing pipes, as well as a design tool implementing them.
\item We showcase a set of examples, enabled by our modeling tool and exploring new points in the design space.
\end{itemize}
\bjoern{I'd say more about the software contribution in the abstract. Maybe that just requires expanding these bullets into a full paragraph.}
